Meta RL analyses

### 2019-02-12 meta_RL_analyses.Rmd
Continuing renaming

```{r}
load_d = function(results_dir, result_subdirs, num_runs, file_type) {
  d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    for (result_subdir in result_subdirs) {
      filename = sprintf("%s%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
      if (!file.exists(filename)) {
        next
      }
      this_d = read.csv(filename, header=T) %>%
        mutate(run = run_i,
               run_type=result_subdir)
      d = bind_rows(d, this_d)
      }
  }
  return(d)
}
```

@@

summary_plot(reward_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
```

@@

```{r}
ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2") +
  facet_wrap(. ~ run_type)
```
```{r}
avg_reward_d %>% filter(is_new_game)
```

@@

```{r}
avg_sweep_d = sweep_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(run_type, size, game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

```{r}
ggplot(avg_sweep_d, aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ run_type)
```

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
                               #"language"
                               ), num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)))
```

```{r}
avg_meta_d = meta_d %>%
  group_by(run_type, run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(run_type, meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
            se_reward = sd_avg_reward/sqrt(n()), 
            ci_lo = avg_avg_reward - 1.96*se_reward, 
            ci_hi = avg_avg_reward + 1.96*se_reward)

@@

```{r}
ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2") +
  facet_wrap(.~run_type)
```

```{r}
summary_plot(meta_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ run_type)

>>>>

```{r}
load_d = function(results_dir, result_subdirs, num_runs, file_type) {
  d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    for (result_subdir in result_subdirs) {
      filename = sprintf("%s%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
      if (!file.exists(filename)) {
        next
      }
      this_d = read.csv(filename, header=T) %>%
        mutate(run = run_i,
               run_type=result_subdir)
      d = bind_rows(d, this_d)
      }
  }
  d = d %>%
    mutate(named_run_type = name_run_type(run_type))
  return(d)
}
```

@@

summary_plot(reward_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ named_run_type)
```

@@

```{r}
avg_reward_d %>% filter(is_new_game)
```

@@

```{r}
avg_sweep_d = sweep_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(run_type, named_run_type, size, game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

```{r}
ggplot(avg_sweep_d, aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ named_run_type)
```

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=named_run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
                               "language", "language_drop_03", "language_drop_05", "language_noncompositional"
                               ), num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)))
```

```{r}
avg_meta_d = meta_d %>%
  group_by(run_type, named_run_type, run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(run_type, named_run_type, meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
            se_reward = sd_avg_reward/sqrt(n()), 
            ci_lo = avg_avg_reward - 1.96*se_reward, 
            ci_hi = avg_avg_reward + 1.96*se_reward)

@@

```{r}
ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2") +
  facet_wrap(. ~ named_run_type)
```

```{r}
summary_plot(meta_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)
